The Radio Sky at Meter Wavelengths: $m$-Mode Analysis Imaging\\ with the Owens Valley Long Wavelength Array

### 2017-10-23 paper.tex
a few more touchups

\newcommand{\astrocaltech}{
    \affiliation{
        Department of Astronomy,
        California Institute of Technology,
        1200 E California Blvd,
        Pasadena, CA 91125
    }
}

\newcommand{\eecaltech}{
    \affiliation{
        Department of Electrical Engineering,
        California Institute of Technology,
        1200 E California Blvd,
        Pasadena, CA 91125
    }
}

\newcommand{\ovro}{
    \affiliation{
        Owens Valley Radio Observatory,
        California Institute of Technology,
        Big Pine, CA 93513
    }
}

\newcommand{\jpl}{
    \affiliation{
        Jet Propulsion Laboratory,
        California Institute of Technology,
        4800 Oak Grove Dr,
        Pasadena, CA 91109
    }
}

\newcommand{\nrao}{
    \affiliation{
        National Radio Astronomy Observatory,
        P.O. Box O,
        Socorro, NM 87801
    }
}

\newcommand{\harvard}{
    \affiliation{
        Harvard-Smithsonian Center for Astrophysics,
        60 Garden Street,
        Cambridge, MA 02138
    }
}

\newcommand{\berkeley}{
    \affiliation{
        University of California Berkeley,
        501 Campbell Hall,
        Berkeley, CA 94720
    }
}

@@

\newcommand{\unm}{
    \affiliation{
        Department of Physics and Astronomy,
        University of New Mexico,
        Albuquerque, NM 87131
    }
}

\newcommand{\vt}{
    \affiliation{
        Bradley Department of Electrical \& Computer Engineering,
        Blacksburg, VA 24061
    }
}

\newcommand{\nvidia}{
    \affiliation{
        NVIDIA Corporation,
        2701 San Tomas Expressway,
        Santa Clara, CA 95050
    }
}

@@

% alphabetical by last name
\author{Benjamin~R.~Barsdell} \harvard \nvidia
\author{Stephen~A.~Bourke}    \astrocaltech
\author{M.~A.~Clark}          \nvidia
\author{Steven~W.~Ellingson}  \vt
\author{Jayce~Dowell}         \unm
\author{Hugh~Garsden}         \harvard
\author{Lincoln~J.~Greenhill} \harvard
\author{Jonathon~Kocz}        \astrocaltech
\author{T.~Joseph~W.~Lazio}   \jpl
\author{Daniel~C.~Price}      \harvard \berkeley \swinburne
\author{Frank~K.~Schinzel}    \nrao \unm
\author{Gregory~B.~Taylor}    \unm
\author{David~P.~Woody}       \ovro

@@

The LWA1 Low Frequency Sky Survey (LLFSS) \citep{2017MNRAS.469.4537D} produced nine maps of the sky
between 35~MHz and 80~MHz. Six of these maps are interior to the frequency range spanned by this
work.  A direct comparison with these LLFSS maps can be seen in Figure~\ref{fig:lwa1-comparison}. In
this figure, the LLFSS maps are filtered to remove the monopole and all modes with $m=0$. The
OVRO-LWA maps are interpolated in frequency and blurred to match the angular resolution of the
corresponding LLFSS map. This comparison uncovered a $\sim45$~arcmin rotation in the LLFSS maps
about the NCP, which is corrected in Figure~\ref{fig:lwa1-comparison}.  60~MHz, the agreement is
generally better than 10\%. However at lower frequencies the agreement deteriorates to about 20\%.
Typically the OVRO-LWA maps have excess emission in the galactic plane and a deficit of emission off
the galactic plane relative to the LLFSS.

@@

In order to understand the effect of polarization leakage, we simulated a point source with 10\%
polarization in Stokes-$Q$ at the location of Cas A.  The simulated visibilities were computed using
the measured beams for $x$- and $y$-dipoles. Because the amplitude of the two beams are not equal in
every direction on the sky, this introduces a direction-dependent leakage of Stokes-$Q$ into
Stokes-$I$. At 73.152~MHz, this leakage is $\lesssim5\%$ above $15^\circ$ elevation, but rapidly
rises to $\gtrsim50\%$ at lower elevations. Cas A is a circumpolar source and spends about seven
hours every day skirting the horizon where the polarization leakage is large, so by placing the
simulated source at the location of Cas A, we are engineering a situation where the polarization
leakage from Stokes-$Q$ into Stokes-$I$ will be large. However, the impact on the unpolarized
$m$-mode analysis maps is mild, amounting to a 0.5\% error in the flux of the source with no
measurable effect on the PSF.

@@

\acknowledgments
This work is dedicated to the memory of Professor Marjorie Corcoran, who was an influential mentor
to M.~W.~Eastwood.

@@

>>>>

\newcommand{\astrocaltech}{
    \affiliation{
        Department of Astronomy,
        California Institute of Technology,
        1200 E California Blvd,
        Pasadena, CA 91125, USA
    }
}

\newcommand{\eecaltech}{
    \affiliation{
        Department of Electrical Engineering,
        California Institute of Technology,
        1200 E California Blvd,
        Pasadena, CA 91125, USA
    }
}

\newcommand{\ovro}{
    \affiliation{
        California Institute of Technology,
        Owens Valley Radio Observatory,
        Big Pine, CA 93513, USA
    }
}

\newcommand{\jpl}{
    \affiliation{
        Jet Propulsion Laboratory,
        California Institute of Technology,
        4800 Oak Grove Dr,
        Pasadena, CA 91109, USA
    }
}

\newcommand{\nrao}{
    \affiliation{
        National Radio Astronomy Observatory,
        P.O. Box O,
        Socorro, NM 87801, USA
    }
}

\newcommand{\harvard}{
    \affiliation{
        Harvard-Smithsonian Center for Astrophysics,
        60 Garden Street,
        Cambridge, MA 02138, USA
    }
}

\newcommand{\berkeley}{
    \affiliation{
        University of California Berkeley,
        501 Campbell Hall,
        Berkeley, CA 94720, USA
    }
}

@@

\newcommand{\unm}{
    \affiliation{
        Department of Physics and Astronomy,
        University of New Mexico,
        Albuquerque, NM 87131, USA
    }
}

\newcommand{\vt}{
    \affiliation{
        Bradley Department of Electrical \& Computer Engineering,
        Blacksburg, VA 24061, USA
    }
}

\newcommand{\nvidia}{
    \affiliation{
        NVIDIA Corporation,
        2701 San Tomas Expressway,
        Santa Clara, CA 95050, USA
    }
}

@@

% alphabetical by last name
\author{Benjamin~R.~Barsdell} \harvard \nvidia
\author{Stephen~A.~Bourke}    \astrocaltech
\author{M.~A.~Clark}          \nvidia
\author{Steven~W.~Ellingson}  \vt
\author{Jayce~Dowell}         \unm
\author{Hugh~Garsden}         \harvard
\author{Lincoln~J.~Greenhill} \harvard
\author{Jonathon~Kocz}        \astrocaltech
\author{T.~Joseph~W.~Lazio}   \jpl
\author{Danny~C.~Price}       \harvard \berkeley \swinburne
\author{Frank~K.~Schinzel}    \nrao \unm
\author{Gregory~B.~Taylor}    \unm
\author{Yuankun~Wang}         \astrocaltech
\author{David~P.~Woody}       \ovro

@@

The LWA1 Low Frequency Sky Survey (LLFSS) \citep{2017MNRAS.469.4537D} produced nine maps of the sky
between 35~MHz and 80~MHz. Six of these maps are interior to the frequency range spanned by this
work.  A direct comparison with these LLFSS maps can be seen in Figure~\ref{fig:lwa1-comparison}. In
this figure, the LLFSS maps are filtered to remove the monopole and all modes with $m=0$. The
OVRO-LWA maps are interpolated in frequency and blurred to match the angular resolution of the
corresponding LLFSS map. This comparison uncovered a $\sim45$~arcmin rotation in the LLFSS maps
about the NCP, which is corrected in Figure~\ref{fig:lwa1-comparison}.  At 60~MHz, the agreement is
generally better than 10\%. However at lower frequencies the agreement deteriorates to about 20\%.
Typically the OVRO-LWA maps have excess emission in the galactic plane and a deficit of emission off
the galactic plane relative to the LLFSS.

@@

In order to understand the effect of polarization leakage, we simulated a point source with 10\%
polarization in Stokes-$Q$ at the location of Cas A.  The simulated visibilities were computed using
the measured beams for $x$- and $y$-dipoles. Because the amplitude of the two beams are not equal in
every direction on the sky, this introduces a direction-dependent leakage of Stokes-$Q$ into
Stokes-$I$. At 73.152~MHz, this leakage is $\lesssim5\%$ above $15^\circ$ elevation, but rapidly
rises to $\gtrsim50\%$ at lower elevations. \citet{2015JAI.....450004O} report similar polarization
leakage measurements with the LWA1.  Cas A is a circumpolar source and spends about seven hours
every day skirting the horizon where the polarization leakage is large, so by placing the simulated
source at the location of Cas A, we are engineering a situation where the polarization leakage from
Stokes-$Q$ into Stokes-$I$ will be large. However, the impact on the unpolarized $m$-mode analysis
maps is mild, amounting to a 0.5\% error in the flux of the source with no measurable effect on the
PSF.

@@

\acknowledgments
This work is dedicated to the memory of Professor Marjorie Corcoran, who was an influential mentor
to MWE.

@@

GBT, JD and FKS acknowledge support from the National Science Foundation under grant AST-1139974.
